Level-Set method on \texttt{p4est}

### 2015-06-19 paper/tex/abstract.tex
Edit abstract

%!TEX root = draft.tex
\begin{abstract}
We present scalable parallel algorithms for the level-set method on adaptive Quadtree and Octree Cartesian grids. The algorithms are based on a \textcolor{red}{domain decomposition technique} and implemented using \texttt{MPI} and the open-source \texttt{p4est} library. We present a scalable parallel semi-Lagrangian method which, similar to its serial implementation, is free of any time-step restrictions. This is achieved by introducing a scalable global interpolation scheme on adaptive tree-based grids. Moreover, we present a simple parallel reinitialization scheme using the pseudo-time transient formulation. Both parallel algorithms scale on the Stampede supercomputer, where we are limited to 4096 cores currently. Finally a relevant application of the algorithms is presented in modeling the crystallization phenomena by solving a Stefan problem, illustrating a level of detail that would be impossible to achieve without a parallel adaptive strategy. We believe that the algorithms presented in this article will be of interest and useful to researchers working with the level-set framework and modeling multi-scale physics in general.
\end{abstract}
\begin{keyword}
Quadtree/Octree Grids \sep Parallel Computing \sep Space Filling Curves \sep Semi-Lagrangian Method \sep Level-set Method
\end{keyword}
\maketitle

>>>>

%!TEX root = draft.tex
\begin{abstract}
We present scalable
% parallel
algorithms for the level-set method on dynamic-adaptive Quadtree and Octree
Cartesian grids. The algorithms are fully parallelized
% on a \textcolor{red}{domain decomposition technique}
and implemented using the \texttt{MPI} standard and the open-source
\texttt{p4est} library.
We solve the level set equation with a semi-Lagrangian method which, similar to
its serial implementation, is free of any time-step restrictions.
This is achieved by introducing a scalable global interpolation scheme on
adaptive tree-based grids.
Moreover, we present a simple parallel reinitialization scheme using the
pseudo-time transient formulation. Both parallel algorithms scale on the
Stampede supercomputer,
% where we are limited to 4096 cores currently.
where we are currently using up to 4096 CPU cores.
Finally, a relevant application of the algorithms is presented in modeling a
crystallization phenomenon by solving a Stefan problem, illustrating a level of
detail that would be impossible to achieve without a parallel adaptive
strategy.
We believe that the algorithms presented in this article will be of interest
and useful to researchers working with the level-set framework and modeling
multi-scale physics in general.
\end{abstract}
\begin{keyword}
Quadtree/Octree Grids \sep Parallel Computing \sep Space Filling Curves \sep
Semi-Lagrangian Method \sep Level-Set Method
\end{keyword}
\maketitle
